Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex

An alternative approach to developing an interface between the task and motion planner is for the task planner to discretize the geometric state space. 
However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems. 
The interface allows the task planner state space to use an abstract state space which ignores geometry. 
The interface layer translates geometric constraints and passes them to the task planner.

@@

In robotics, it is often necessary to create a plan for a series of motions of the robot in order to complete some high level plan.
In order to find a task plan which is actually feasible, the task planner must have some knowledge of the geometry of the world.
Without knowledge of the actual spatial configurations of objects in the world, the task planner would create plans where some actions cannot be completed, due to infeasible motion plans from blocking objects or interference between the robot and the environment.

The high level problem this implementation addresses is to create a combined task and motion planner, following that presented in [1].  
This approach allows the motion planner to give information to the task planner and allows us to keep the continuous variables continuous, rather than discretizing.  
This prevents a combinatorial explosion of the state space that the task planner needs to search over.

>>>>

An alternative approach to developing an interface between the task and motion planner is for the task planner to discretize the geometric state space. 
However, the number of required discretizations to solve the problem is generally very large and results in extremely large or infeasible problems. 
An interface allows the task planner state space to use an abstract state space which ignores geometry. 
The interface layer translates geometric constraints and passes them to the task planner.

@@

In robotics, it is often necessary to create a plan for a series of motions of the robot in order to achieve some high level objective.
In order to find a task plan which is actually feasible, the task planner must have some knowledge of the geometry of the world.
Without knowledge of the actual spatial configurations of objects in the world, the task planner would create plans that could not complete some actions, due to infeasible motion plans from blocking objects or interference between the robot and the environment.

The high level problem this implementation addresses is to create a combined task and motion planner, following that presented in [1].  
This approach allows the motion planner to give information to the task planner and keeps continuous variables continuous, rather than discretizing.  
This prevents a combinatorial explosion of the state space that the task planner needs to search over.
